\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Accelerating DataLog applications with cuDF \\
% {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
% should not be used}
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{
\IEEEauthorblockN{Ahmedur Rahman Shovon}
\IEEEauthorblockA{\textit{University of Alabama at Birmingham} \\ ashovon@uab.edu }
\and
\IEEEauthorblockN{Landon Richard Dyken}
\IEEEauthorblockA{\textit{University of Alabama at Birmingham} \\ ldyken53@uab.edu }
\and
\IEEEauthorblockN{Thomas Gilray}
\IEEEauthorblockA{\textit{University of Alabama at Birmingham} \\ gilray@uab.edu }
\and
\IEEEauthorblockN{Oded Green}
\IEEEauthorblockA{\textit{Nvidia} \\ ogreen@nvidia.com }
\and
\IEEEauthorblockN{Sidharth Kumar}
\IEEEauthorblockA{\textit{University of Alabama at Birmingham} \\ sid14@uab.edu }
}

\maketitle

\begin{abstract}
Datalog, a bottom-up declarative logic programming language, extends its application in graph mining, program analysis, machine learning, and deductive databases. An example of logical inference is the transitive closure computation of a graph. The transitive closure computation in Datalog is compiled into iterated relational algebra consisting of union, projection, and join operations. Pandas is a popular data analysis package that provides relational algebra functionalities. GPU (Graphics Processing Unit) programming has been accelerating high-performance computing research in recent years by leveraging the massive GPU parallelism. cuDF is a library from the Rapids suite that uses the NVIDIA CUDA (Compute Unified Device Architecture) programming model for GPU parallelism. It provides similar functionalities to Pandas. In this paper, we analyze and evaluate the performance of cuDF versus Pandas to compute the transitive closure of real-world and synthetic graphs from SNAP datasets. Finally, we discuss the prospect of developing a scalable backend for Datalog. 
\end{abstract}

\begin{IEEEkeywords}
relational algebra, transitive closure, cudf, datalog
\end{IEEEkeywords}

\input{sections/introduction}
\input{sections/background}
\input{sections/implementation}
\input{sections/evaluation}
\input{sections/conclusion}

\bibliographystyle{IEEEtran}
\bibliography{sc}

\end{document}
